\textbf{Access Control for Content Distribution Network Assets}

### 2016-06-14 tex/paper.tex
Added the last changes according to the comments

\par All files are also stored directly in MongoDB with the help of GridFS. GridFS chunks the files
according to the size limit of MongoDB objects, which is currently 4MB. The advantage of storing
files directly in the database rather than in the filesystem is that backups of can be done through
a database backup which will contain both the meta-data stored in MongoDB and the files which
results in that no separate files needs to be backed up.  Another advantage is that you can retrieve
specific ranges of a file, although that feature is not needed in the Perius implementation. For
scalability this could be used to retrieve different parts of a file from different servers, normal
load balancing would probably work better in a system like Perius where no extremely large files are
expected to be stored.

@@

As can be seen in Listing~\ref{CONTAINERPOSTREQUEST} the server can handle around 4000 container
POST requests per second. The problem that this test resulted in was not the amount of containers
that could be posted, but rather loading all those containers in the interface or API afterwards.
When requesting the project that the containers were posted to the web server timed out the request,
as it took too long for the back-end to build the project tree. In this work, the web server will
not  
be configured to accept longer data processing time, as trees as large as this for a single project
will not be used in production.

@@

\subsubsection{Authentication}
The authentication of users in the system is currently being handled by LDAP~\cite{LDAP}, as Perius 
is mainly focussed at being deployed in internal networks which usually has an LDAP service enabled. 
LDAP also makes it easier for the user to login as no separate account is needed for Perius and 
thus the user can use the same account as for all the LDAP connected services on the internal 
network.

\subsubsection{Audit logs}
Audit logs are used in the system to keep track of which users that perform which actions. In the
event that somebody, consciously or unconsciously, are leaking private CDN content from within the
organisation using Perius. The audit trail can then be used to find which LDAP account that was
responsible for the leak.

\subsubsection{CDN Connections} \label{sec:cdn_connections}
When uploading files to the CDN networks, their TLS/SSL protected APIs are used to ensure that no
data leaks through packet sniffing etc. The files are grouped corresponding to their parent
containers in Perius, which makes it possible to handle the security settings for all files in a
group at once, without having to manually traverse through the tree in Perius.

@@

\par \textbf{IP range restriction} \\
The IP range restriction is presented as a third option in Perius, even though it in fact is just a
part of a Signed Cookie or URL policy. The IP range restriction makes it possible to restrict which
IP addresses that can access the asset, this option can be fitting when for example an office or
companies internet access is based on a set of public static IP addresses and thus restricts the
content from ever being accessed outside of that controlled network.

@@

\subsubsection{Security}
The greatest security improvement of Perius compared to its predecessor Battlebinary is not the
security of the system itself but rather how Perius handles the contents security settings on the
CDN providers. Perius uses several of the security features for private content that the CDN
providers offer (see Section~\ref{sec:private_content}) to make sure that the content only is
accessible from where it should be. In Perius it is possible to have three different modes for a CDN
asset; public to all, only accessible from certain IP ranges or only accessible by clients using a
signed URL or cookie. In Battlebinary the content was secured by adding a part of the hash of the
file (see Section~\ref{sec:current_system}) to the filename that it was uploaded with, which
resulted in a URL on the CDN that was not guessable but if the link somehow leaked the content that
the link referred to would be open to anyone.

@@

When using the ReactiveMongo driver~\cite{REACTIVEMONGO}, which is asynchronous and non-blocking, 
the application has no limits of how much load and users it can handle as the hardware and nodes 
can be scaled up linearly when needed. With Cashbah~\cite{CASBAH}, which is used with the current 
implementation, it is harder to scale to the enormous amounts of load which ReactiveMongo can 
support as Casbah is synchronous and has blocking IO. For this work the kind of scalability which 
is offered by ReactiveMongo is not needed as the load will not reach the peak, as discussed in 
Section~\ref{sec:GET_REQUESTS}, for what Casbah can handle on a single server.

\subsubsection{Load Testing}
Section~\ref{sec:load_testing}, specifically Listing~\ref{OKREQUEST}, shows that the HTTP server can
answer about 100K requests/s when not involving any payload other than status code 200 (OK). When
comparing that to the request which involved the server responding with a small (100 Byte) payload
(Listing~\ref{STATICREQUEST}) one can see that it is about 10\% slower to send some more data,
\textasciitilde90K requests/s. However when comparing that to the requests that needed database
access it is obvious that the HTTP server can handle all the load that it needs to, as
Listing~\ref{DBREQUEST} shows that to fetch all documents in a collection (in this case only one) is
dramatically slower, the throughput was only \textasciitilde7000 requests/s.

@@

\subsection{Persistent Storage}
More research could have been done in the choosing of persistent storage, as mentioned in 
\textit{``NoSQL: Moving from MapReduce Batch Jobs to Event-Driven Data Collection''}
~\cite{KLINGSBO} many applications that choose NoSQL databases as their persistent storage 
actually do not need it. This is most likely true for Perius too, it would have been efficient 
enough generating the project trees from an indexed SQL database with foreign keys. On the 
other hand it was quite nice having the BSON documents for insertion as they were so similar 
to the accepted JSON format from the REST service. As Perius most common operations involve 
modifying project trees, a graph database should have been researched too.

\subsection{Copy-on-Write's effect on Scalability}
As no comparison with solutions that were not Copy-on-Write based were made, no scientific
conclusions can be drawn from what its effect was on the scalability of the system. However some
intuitively drawn conclusions can be suggested. If comparing to a system which uses a SQL database
the Copy-on-write system would have an easier time to scale on the width as no global locks or
transactions has to be used, which with high probability would slow down the system, especially when
widely distributed.
The gain of having the locks or transactions would be that the system would
always be in a fully consistent state. The loss would be that all of the database nodes would need
to constantly have to, in some sense, be fully aware of the state of the other nodes.
Sharding~\cite{SHARDING} could be used to minimise the communication of state between the nodes, but
that results in less fault tolerance and possibly higher loads on some nodes than others due to that
the data most likely will not be accessed uniformly.

@@

\subsection{Branching}
Branching was also implemented in Perius, but to not make the report too wide it was not included.
The branching worked by the user selecting a container that the branch should be based on and a
container in which the branch should be places. The user could then choose which containers and
content that it wanted to update with the origin source of and which objects that should be deep
copied to the new branch.

@@

\subsubsection{Front-end Refactorization}
Currently the implementation fetches the full project tree every time a change is made. This results
in increased latency, bandwidth usage and server load. We propose a refactorization of the front-end
where it updates the state according to the REST response of each modification to the project tree
instead of re-fetching it.

>>>>

\par All files are also stored directly in MongoDB with the help of GridFS. GridFS chunks the files
according to the size limit of MongoDB objects, which is currently 4MB. The advantage of storing
files directly in the database rather than in the filesystem is that backups of can be done through
a database backup which will contain both the meta-data stored in MongoDB and the files which
results in that no separate files needs to be backed up.

@@

As can be seen in Listing~\ref{CONTAINERPOSTREQUEST} the server can handle around 4000 container
POST requests per second. A problem that was discovered during this test was not the amount of
containers that could be posted, but rather loading all those containers in the interface or API
afterwards. When requesting the project tree from the web server it timed out the request
since it took too long for the back-end to build the tree. In this work the web server will not be
configured to accept longer data processing time, due to the low probability of trees as large as
this being used in production.

@@

\subsubsection{Authentication}
The authentication of users in the system is currently being handled by LDAP~\cite{LDAP}, since
Perius mainly will be deployed in internal networks with an existing LDAP infrastructure.  LDAP also
makes it easier for the user to login as no separate account is needed for Perius and thus the user
can use the same account as for all the LDAP connected services on the internal network.

\subsubsection{Audit logs}
Audit logs are used in the system to keep track of which users have perform which actions. In the
event that somebody, consciously or unconsciously, are leaking private CDN content the audit trail
can then be used to find which LDAP account that was responsible for the leak.

\subsubsection{CDN Connections} \label{sec:cdn_connections}
When uploading files to the CDN networks, their TLS/SSL protected APIs are used to ensure that no
data leaks through packet sniffing etc. The files are grouped corresponding to their parent
containers in Perius, which makes it possible to handle the security settings for all files in a
group at once, without having to manually traverse the tree in Perius.

@@

\par \textbf{IP range restriction} \\
The IP range restriction is presented as a third option in Perius, even though it in fact is just a
part of a Signed Cookie or URL policy. The IP range restriction makes it possible to restrict which
IP addresses that can access the asset, this option can be fitting when for example an office or
a restricted groups internet access is based on a set of public static IP addresses.

@@

\subsubsection{Security}
The greatest security improvement of Perius compared to its predecessor Battlebinary is not the
security of the system itself but rather how Perius handles the content security settings on the
CDN providers. Perius uses several of the security features for private content that the CDN
providers offer (see Section~\ref{sec:private_content}) to make sure that the content only is
accessible from where it should be. In Perius it is possible to have three different modes for a CDN
asset; public to all, only accessible from certain IP ranges or only accessible by clients using a
signed URL or cookie. In Battlebinary the content was secured by adding a part of the hash of the
file (see Section~\ref{sec:current_system}) to the filename that it was uploaded with, which
resulted in a URL on the CDN that was not guessable but if the link somehow leaked the content that
the link referred to would be open to anyone.

@@

When using the ReactiveMongo driver~\cite{REACTIVEMONGO}, which is asynchronous and non-blocking,
the application has no limits of how much load or how many users it can handle as the hardware and
nodes can be scaled up linearly when needed. With Cashbah~\cite{CASBAH}, which is used in the
current implementation, it is harder to scale to the enormous amounts of load that ReactiveMongo
can support as Casbah is synchronous and has blocking IO. For this work the kind of scalability
which is offered by ReactiveMongo is not needed as the load will not reach the peak, as discussed in 
Section~\ref{sec:GET_REQUESTS}, for what Casbah can handle on a single server.

\subsubsection{Load Testing}
Section~\ref{sec:load_testing}, specifically Listing~\ref{OKREQUEST}, shows that the HTTP server can
answer about 100K requests/s when not involving any payload other than status code 200 (OK). When
comparing that to the request which involved the server responding with a small (100 Byte) payload
(Listing~\ref{STATICREQUEST}) one can see that it is about 10\% slower to send some more data,
\textasciitilde90K requests/s. However when comparing that to the requests that needed database
access it is obvious that the HTTP server can handle all the load that it needs to, as
Listing~\ref{DBREQUEST} shows that to fetch all documents in a collection (in this case only one) is
dramatically slower, the throughput was only $\approx$7000 requests/s.

@@

\subsection{Persistent Storage}
More research could have been done in the choosing of persistent storage, as mentioned in many
applications that choose NoSQL databases as their persistent storage actually do not need
it~\cite{KLINGSBO}. This is most likely true for Perius too: it would have been efficient enough
generating the project trees from an indexed SQL database with foreign keys. On the other hand it
was quite nice having the BSON documents for insertion as they were so similar to the accepted JSON
format from the REST service. As Perius most common operations involve modifying project trees, a
graph database should have been researched too.

\subsection{Copy-on-Write's effect on Scalability}
Since no comparison with solutions that were not Copy-on-Write based were made, no scientific
conclusions can be drawn from what its effect was on the scalability of the system. However some
intuitively drawn conclusions can be suggested. If comparing to a system which uses a SQL database
the Copy-on-write system would have an easier time to scale since no global locks or transactions
has to be used, which with high probability would slow down the system, especially when widely
distributed.
The gain of having the locks or transactions would be that the system would
always be in a fully consistent state. The loss would be that all of the database nodes would need
to constantly have to, in some sense, be fully aware of the state of the other nodes.
Sharding~\cite{SHARDING} could be used to minimise the communication of state between the nodes, but
that results in less fault tolerance and possibly higher loads on some nodes than others due to that
the data most likely will not be accessed uniformly.

@@

\subsection{Scalability}
Since GridFS was used to store the files an unexplored option for making it easier to scale is to
use GridFS feature of retrieving specific ranges of a file. For scalability this could be used to
retrieve different parts of a file from different servers, but normal load balancing would probably
work better in a system like Perius where no extremely large files are expected to be stored.

\subsection{Branching}
Branching was also implemented in Perius, but to not make the report too broad it was not included.
The branching worked by the user selecting a container that the branch should be based on and a
container in which the branch should be placed. The user could then choose which containers and
content that it wanted to update with the origin and which objects that should be deep
copied to the new branch.

@@

\subsubsection{Front-end Refactorization}
Currently the implementation fetches the full project tree every time a change is made. This results
in increased latency, bandwidth usage and server load. We propose a refactorization of the front-end
where it updates the state according to the REST response of each modification to the project tree
instead of fetching the whole tree again.
